Recommendations for Intelligent Code Reorganization

### 2016-08-31 Manuscript.tex
Updates from ShareLaTeX

		% \title{How to Discourage Useless Refactorings}
		\title{Recommendations For Intelligent Code Reorganization}

@@

			\noindent
			{\bf Method: } We introduce XTREE, a tool that analyzes a historical log of defects seen previously in the code and generates a set of useful\footnote{Need to define useful in precise terms} code changes.
			Any bad smell that requires changes outside of that set can be deprioritized (since there is no historical evidence that the bad smell causes any problems).

@@

			\noindent
			{\bf Conclusion: }
			Before undertaking a code reorganization based on a bad smell report,
			use a tool like XTREE to check and ignore any code reorganizations   that  are useless; i.e. which lacks evidence
			in the historical record  that it is useful to make that change.
			Note that this use case applies to both manual code reorganizations proposed by developers
			as well as refactoring  conducted by automatic methods.
			This recommendation assumes that there is an historical record.
			If none exists, then the results of this paper could be use used as a guide (see our
			Table~8).

@@

	According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
	are ``a surface indication that usually corresponds to a deeper problem''.
	Fowler strongly recommends   removing   code smells   by
	\begin{quote}
		``...applying a series of small behavior-preserving transformations, each 
		of which seem ``too small to be worth doing''. 
		The  effect of   these \underline{refactoring} transformations is quite significant. By doing them in small steps you reduce the risk 
		of introducing errors''.
	\end{quote}

	Bad smells are a widely used technique for evaluating code. While the original bad small concept was largely subjective~\cite{fowler99}, researchers including Marinescu~\cite{marinescu06} and others has provided formal definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics. Consequently, code smells are captured by popular static analysis tools such as PMD\footnote{https://github.com/pmd/pmd}, CheckStyle\footnote{http://checkstyle.sourceforge.net/}, FindBugs\footnote{http://findbugs.sourceforge.net/}, and SonarQube\footnote{http://www.sonarqube.org/}, although not always explicitly labeled as such.

	Refactoring bad smells from code is generally accepted as a recommended practice, but code reorganization by definition does not change the external functionality of the system and thus may have no perceived value. For example, this paper began when a Washington-based software company shared one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code. 
	%This management team wanted some way to check if all that activity was useful. 
	Kim et al.\cite{kim2012field} surveyed developers at Microsoft and found that refactoring incurs significant cost and risks. A Google search on the terms ``refactoring cost'' yields numerous threads on StackOverlfow from developers asking how to justify refactoring and when the costs of refactoring outweight its benefits.

@@

	% In addition to tools that capture bad smells such as FindBugs and SonarQube, a multitude of tools have been proposed to support refactoring (e.g., \cite{ge2014manual,lee2013drag,foster2012witchdoctor,ge2012reconciling}). Note that these managers are {\em not} asking for better
	% automatic refactoring
	% tool support. 
	% Their human programmers are refactoring
	% code all the time, perhaps too much so.
	% Hence, the management goal
	The challenge is to encourage code reorganizations that result in perceivable benefits (such as reduced defect proneness or lower maintenance costs) and avoid code reorganizations with no demonstrable benefit and thus waste effort.

	This paper describes one approach to evaluate whether code reorganizations that change the structure of code are likely to have a perceivable benefit by evaluating:
	\bi
	\item If there is no evidence in the historical record that changing ``X'' is useful;
	\item Then discourage developers from doing ``X''.
	\ei
	We use data mining to generate two oracles: a {\em primary
		change oracle} and a {\em secondary verification oracle}.
	By combining these two oracles,
	we can generate and validate useful
	changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klockwork\footnote{http://www.klocwork.com/}.

	In this paper, we use 
	the XTREE cluster delta algorithm as the {\em primary change  oracle}.
	XTREE 
	explores the historical record of a project to find clusters of module.
	It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects $C_1$ (so $\Delta$
	is some subset of $C_1 - C_0$). % To define ``minimal'', XTREE uses an entropy measure.

	As to 
	the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
	sensible changes. For this purpose we use Random Forest~\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
	In our framework,  learning
	the secondary oracle is   a {\em separate} task from that of learning the primary
	oracle. This  ensures that the verification oracle offers an independent
	opinion on the value of the proposed changes.

	When these oracles were applied to defect data from
	open source object-oriented software systems, we discovered a {\em conjunctive fallacy}
	in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.
	A common heuristic is to recommend code reorganization of ``bad'' code
	to make it ``better'' as follows: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded. That is:
	\begin{equation}\label{eq:df}
		\scriptstyle
		\begin{array}{rl}
			\mathit{bad}    & = \left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee    ...                             \\
			\mathit{better} & = \neg\;\mathit{bad} = \left(a_1 \le t_1 \right) \bigwedge \left(a_2 \le t_2\right)  \bigwedge  ... 
		\end{array}
	\end{equation}
	We say that the above definition of ``better'' is a conjunctive fallacy
	since it assumes that the best way to improve code is to decreases multiple code attribute measures below $t_i$ in order
	to remove the ``bad'' smells. In reality, there exists an intricate set of associations between static code measures
	such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
	It is easy to see why this is so.
	A requirement for  code reorganization is that the new code supports the same functionality
	as before. If we pull code out of a function (since that function has grown too
	large), {\em that functionality has to go somewhere else}. What we see in XTREE's change
	recommendation is that if we decrease a module's lines of code  then in the refactored
	code, the functionality is achieved via a communication between several different parts
	of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
	that module's coupling metrics.

	\subsection{Structure of this Paper}

	This paper  claims that (a)~XTREE is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous code reorganizations since they usually refer to a very 
	small subset of the static code measures (which allows us to rule out code reorganizations based on any of the omitted
	static code measures). 
	In support of these claims, 
	the rest of this paper is structured as follows. In Section~2, we offer some background on bad smells. In Section~3, 
	different methods are presented for determining when code does/does not have bad smell. One of those methods
	will be XTREE while the others will come from other researchers. Section~4
	defines an assessment method that checks which of these methods is most useful. The results from that assessment 
	are presented in Section~5. Those results will answer five research questions.

	{\bf  RQ1: Effectiveness}\footnote{test}: According to the verification oracle, which of the methods  defined in Section~3 is the best  change oracle for identifying what and how
	code modules should be changed? To answer this question, we used data from five OO Java projects
	(Ivy, Lucene, Ant, Poi, Jedit). It was found that:
	\begin{lesson}
		XTREE is the most accurate oracle on how to change code modules in order to reduce defects.
	\end{lesson}

	{\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
	ignore irrelevant bad smell detectors.  If those changes are minimal (i.e. affect fewest attributes) then those changes
	will be easiest to apply and monitor. Hence, we ask, which of the Section~3 methods recommended changes to the fewest
	code attributes?
	\begin{lesson}
		Of all the code change oracles studied here, XTREE recommends the fewest number of changes to static code measures.
	\end{lesson}

	{\bf RQ3: Stopping}: Our advice to managers is to discourage code reorganization based on changes that lack
	historical evidence of being effective. How effective is XTREE at offering such ``stopping points'' (i.e. clear guidance on what {\em not} to do)??
	\begin{lesson}
		In  any  project,  XTREE's  recommended  changes  only  mentions one to four 
		of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
		would hence be deprecated.
	\end{lesson}

	{\bf RQ4: Stability}: Across different projects, how variable are the changes recommended by our best change oracle?
	\begin{lesson}
		The direction of change recommended by XTREE is  very stable across repeated runs of the program 
	\end{lesson}

	{\bf RQ5: Conjunctive Fallacy}:  
	Is it always  useful  to aplly \eq{df}; i.e. make code better by   reducing the values of  multiple code attributes? We find that:
	\begin{lesson}
		XTREE usually recommends reducing lines of code (size of the modules).
		That said,  XTREE often recommends {\em increasing} the values of other static code attributes.
	\end{lesson} 
	Note that {\bf RQ3, RQ4, RQ5} 
	confirms the intuitions
	of the project managers that prompted this investigation:
	\bi
	\item
	Yes,  indeed, their programmers
	were wasting time on   performing code reorganizations  that  decreased multiple measures when, in fact,
	they should be trying to {\em decrease} some measures while {\em increasing} others.
	\item
	Across all studied projects, XTREE found that  around one-fifth  
	of the measures were usually found within  change recommendations. That is, it is 80\% likely that
	that code reorganization based on reducing any one measurement picked at random will be useful.
	\ei
	Consequently, we  recommend the following use case for  XTREE:
	\bi
	\item Before doing  code reorganization based on a bad smell report...
	\item ...check and discourage any code reorganization   for which there is no proof
	in the historical record that the change improves the code.
	\ei
	This use case described  applies to both manual code reorganizations proposed by developers
	as well as refactoring conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
	code refactoring by discouraging refactorings for useless goals.

	\subsection{Relationship to Prior Work }
	A four page preliminary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies on only two  of
	the five data sets studied here. Also, that prior work had:
	\bi
	\item
	no comparison to any baseline
	method from other researchers, whereas this paper compares XTREE's recommendations
	with those found by researchers exploring bad smells.
	\item
	no {\em secondary verification oracle}, i.e. no way to check if XTREE's recommended changes were sensible.
	\ei
	Further, of this entire paper, the only sections containing material
	found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of the results in \fig{jur}.

@@

	Much research endorses them to guide
	code improvement (e.g., code reorganization or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
	lists dozens of papers on smell detection and repair tools. 
	Yet
	other papers cast doubt on the value of bad smells
	as triggers for code improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}. 
	As we show in this paper,  
	tools, text books, and developers disagree on what bad smells
	are important enough to hunt down and eliminate. Our findings
	are consistent with other research suggesting that universal bad
	smells that ignore project context are not useful to guide refactoring~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

	If the SE literature is contradictory, why not ignore it and use domain experts (software engineers) to decide
	what bad smells to fix? We do not recommend this since developer {\em cognitive biases} can mislead them to
	assert that some things are important and relevant when they are not. 
	A widespread malaise in software engineering is that
	beliefs about software are rarely revised and hence may be
	inaccurate and 
	misleading~\cite{passos11,jorgensen09,mei15,me16phase,prem16}. Software developers may have strong views on many issues, including bad smells, but those views may be wrong for the current
	project.
	Software engineering is not the only field with this problem.
	For example, the medical profession applies many practices based on studies that have been disproved (a recent article in the Mayo Clinic Proceedings~\cite{prasad13} found 146 medical practices based on studies in year i, but which were reversed by subsequent trials within years i + 10). Even when the evidence for or against a treatment or intervention is clear, medical providers and patients may not accept it~\cite{aschwanden10}. Aschwanden warns that {\em cognitive biases} such as confirmation bias (the tendency to look for evidence that supports what you already know and to ignore the rest) influence how we process information~\cite{aschwanden15}.

@@

	\bi
	% COMMENT FROM LL: This bullet is weak. Maybe goto isn't used in an unrestricted manner because of Djikstra's warning.
	% \item
	% Nagappan et al. analyzed~\cite{mei15} 
	% how   {\tt goto}  was used  in 11,000 Github repositories. 
	% They found that developers
	% rarely used {\tt goto} in the unrestricted manner that alarmed Dijkstra in his  1968
	% memo ``Go to statement considered harmful''~\cite{Dijkstra68}.
	\item
	In other work~\cite{me16phase} with the Software Engineering Institute (SEI), we have revisited
	the ``phase delay'' truism that {\em the cost of fixing an error dramatically increases the longer it is in the system}. 
	We found no evidence for such large   phase delay effect in modern
	software (in 171 software projects shepherded
	by the SEI, 2006-2014) possibly since it has been  heavily mitigated by $21^{st}$ century software development languages, tools and development practices. 
	Whatever the reason, the main point  is that phase delay is a widely
	held belief, despite little recent evidence to support it.
	\item
	Devanbu et al. examined responses from 564 Microsoft software developers from around
	the world, they found that  ``(a)~programmers do indeed have very
	strong beliefs on certain topics; (b)~their beliefs are primarily formed
	based on personal experience, rather than on findings in empirical
	research; (c)~beliefs can vary with each project, but do not necessarily
	correspond with actual evidence in that project''~\cite{prem16}.
	\ei
	Devanbu et al. further  comment that ``programmers give personal experience
	as the strongest influence in forming their opinions''. This is a troubling
	result, especially given the above comments from Passos and  J{\o}rgensen et al.~\cite{passos11,jorgensen09} about how quickly practitioners form, freeze, and rarely revist those opinions.

@@

	If the above remarks hold true for bad smells, then we would expect
	to see much disagreement on which bad smells are important and relevant
	to  a particular project. This is indeed the case.
	The first column of \fig{smells} 
	lists  commonly mentioned bad smells and comes from Fowler's 1999 text~\cite{fowler99} and a subsequent 2005 text by Kerievsky that is widely cited~\cite{Kerievsky2005}.
	The other
	columns show data from other studies on which bad smells matter most.
	The columns marked as Lanza'06 and Yamashita'13 are from peer reviewed literature. The column maked SonarQube is a popular open source
	code assessment tool that includes detectors for six of the bad smells
	in column one. 
	The {\em developer survey} (in the right-hand-side column) shows the results of an hour-long whiteboard sessions with a group of 12 developers from a Washington
	D.C. web tools development company. Participants
	worked in a round robin manner to rank the bad smells they thought were
	important (and any disagreements were discussed with the whole group).
	Amongst the group, there was  some
	consensus on  the priority of which bad smells to fix
	(see the annotations VH=very high,
	H=high, L=low, VL=very low, and ``?''= no consensus).

@@

	A  blank cell in \fig{smells}
	indicates where   other work has chosen to ignore
	one of the bad smells in column one. 
	Note that most of the cells are blank, and that the studies ignore the majority of the Fowler bad smells.
	SonarQube has no detectors for many of the column one bad smells.
	Also, nearly half the Yamashita list of bad smells
	does not appear in the Fowler and Kerievsky list. The eight numbers
	in the  Yamashita'13 column show the rankings for the bad smells 
	that overlap with Fowler and Kerievsky; Yamashita also discussed other smells not covered in Fowler'99.

	Two of the studies in \fig{smells} offers some comments on the relative importance
	of the different bad smells in the Yamashita'13 study and the developer study. Three of the bad smells listed in the top half of the Yamashita'13 rankings also score very high in the developer survey. Those three were {\em duplicated code, large class}, 
	and {\em long method}. 
	Note that this agreement also means that the
	Yamashita'13 study and the developer survey   
	believe
	that very few  code smells are   high priority issues
	requiring code reorganization.

@@

	Having made the case for automatic support for assessing bad smells,
	this section reviews different ways for building those tools (one of those tools,
	XTREE, will be our recommended {\em primary change oracle}).
	Later in this paper, we will offer  a {\em secondary verification oracle}
	that checks the effectiveness of the changes proposed by XTREE.

	The SE literature offers two ways of learning bad smell thresholds.
	One approach relies on 
	{\em outlier statistics}~\cite{erni96,bender99}. This approach
	has been used   by Shatnawi~\cite{Shatnawi10}, Alvenes et al.~\cite{Alves2010}
	and Hermans et al.~\cite{hermans15}.
	Another approach is 
	based on {\em cluster deltas} that we developed
	for   Centroid Deltas~\cite{me12c} and 
	use here for XTREE. 
	These two approaches are discussed below.

@@

	\input{xtree_tut.tex}

@@

	\subsubsection{ Shatnawi}
	Shatnawi~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
	is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
	constants to compute the thresholds which, following Shatnawi's guidance, we set to
	$p_0=p_1=0.05$.

>>>>

		\title{Recommendations for Intelligent Code Reorganization}

@@

			\noindent
			{\bf Method: } We introduce XTREE, a tool that analyzes a historical log of defects seen previously in the code and generates a set of useful code changes.
			Any bad smell that requires changes outside of that set can be deprioritized (since there is no historical evidence that the bad smell causes any problems).

@@

			\noindent
			{\bf Conclusion: }
			Before undertaking a code reorganization based on a bad smell report,
			use a tool like XTREE to check and ignore any such operations that  are useless; i.e. which lacks evidence
			in the historical record  that it is useful to make that change.
			Note that this use case applies to both manual code reorganizations proposed by developers
			as well as those conducted by automatic methods.
			This recommendation assumes that there is an historical record.
			If none exists, then the results of this paper could be use used as a guide (see our
			Table~8).

@@

	According to   Fowler~\cite{fowler99}, bad smells (a.k.a. code smells)
	are ``a surface indication that usually corresponds to a deeper problem''.
	Fowler  recommends   removing   code smells   by
	\begin{quote}
		``...applying a series of small behavior-preserving transformations, each 
		of which seem ``too small to be worth doing''. 
		The  effect of   these refactoring transformations is quite significant. By doing them in small steps you reduce the risk 
		of introducing errors''.
	\end{quote}

% 	Bad smells are a widely used technique for evaluating code. 
	While the original concept of bad smells was largely subjective, researchers including Marinescu~\cite{marinescu06} and Munro~\cite{munro2005product} provide definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics. Consequently, code smells are captured by popular static analysis tools such as PMD\footnote{https://github.com/pmd/pmd}, CheckStyle\footnote{http://checkstyle.sourceforge.net/}, FindBugs\footnote{http://findbugs.sourceforge.net/}, and SonarQube\footnote{http://www.sonarqube.org/}.

	The value of correcting bad smells is not always perceivable. For example, this paper began when a Washington-based software company shared one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code. Kim et al.~\cite{kim2012field} surveyed developers at Microsoft and found that code reorganizations incur significant cost and risks. Researchers are actively attempting to demonstrate the actual costs and benefits of fixing bad smells~\cite{nugroho2011empirical,zazworka2011prioritizing,zazworka2013case}, though more case studies are needed.

			We refer to the process of removing bad smells as \textit{code reorganization}. Code reorganization is an amalgum of perfective and preventive maintenance~\cite{iso14764}. In contrast to refactoring, code reorganization is not guaranteed to preserve behavior.

	Fowler~\cite{fowler99} and other influential software practitioners~\cite{mcconnell2004code,horror} recommend refactoring and code reorganization to remove bad smells. Experiments suggest a relationship between code smells and poor maintainability or defect proneness~\cite{yamashita2013code,yama13,zazworka2011investigating}, though these findings are not always consistent~\cite{olbrich2010all}. In this paper, we focus on the challenge of recommending code reorganizations that result in perceivable benefits (such as reduced defect proneness) and avoid those reorganizations which have no demonstrable benefit and thus waste effort.

	%A Google search on the terms ``refactoring cost'' yields numerous developer questions on StackOverflow asking how to justify bad smell removal and when the costs outweigh the benefits.

@@

	% In addition to tools that capture bad smells such as FindBugs and SonarQube, a multitude of tools have been proposed to support refactoring (e.g., \cite{ge2014manual,lee2013drag,foster2012witchdoctor,ge2012reconciling}). Note that these managers are {\em not} asking for better
	% automatic refactoring
	% tool support. 
	% Their human programmers are refactoring
	% code all the time, perhaps too much so.
	% Hence, the management goal

	This paper evaluates XTREE~\cite{krishna2015actionable}, a framework to evaluate whether a code reorganization is likely to have a perceivable benefit in terms of defect-proneness. We focus on bad smells indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klockwork\footnote{http://www.klocwork.com/}. 
		XTREE examines the historical record of code metrics for a project. If there is no evidence that changing code metric ``X'' is useful (e.g., lowering ``X'' reduces defect-proneness), then developers should be discouraged from wasting effort on that change.
	% 	\bi
% 	\item If there is no evidence in the historical record that changing ``X'' is useful;
% 	\item Then discourage developers from doing ``X''.
% 	\ei

	We use data mining to generate two oracles: a {\em primary
		change oracle} and a {\em secondary verification oracle}.
	By combining these two oracles,
	we can identify and validate useful
	code reorganizations.

	We use 
	the XTREE cluster delta algorithm as the {\em primary change  oracle}.
	XTREE 
	explores the historical record of a project to find clusters of modules (e.g., files or binaries).
	It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects $C_1$ (so $\Delta$
	is some subset of $C_1 - C_0$). % To define ``minimal'', XTREE uses an entropy measure.

	The {\em secondary verification oracle} checks if the primary oracle is proposing
	sensible changes. We create the verification oracle using Random Forest~\cite{breiman2001random} augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
	In our framework,  learning
	the secondary oracle is   a {\em separate} task from that of learning the primary
	oracle. This  ensures that the verification oracle offers an independent
	opinion on the value of the proposed changes.

	An advantage to the XTREE cluster delta approach is that it avoids the 
% 	When these oracles were applied to defect data from
% 	open source object-oriented software systems, we discovered a 
	{\em conjunctive fallacy}.
	A common heuristic in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15} is: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded. That is:
	\begin{equation}\label{eq:df}
		\scriptstyle
		\begin{array}{rl}
			\mathit{bad}    & = \left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee    ...                             \\
			\mathit{better} & = \neg\;\mathit{bad} = \left(a_1 \le t_1 \right) \bigwedge \left(a_2 \le t_2\right)  \bigwedge  ... 
		\end{array}
	\end{equation}
	We say that the above definition of ``better'' is a conjunctive fallacy
	since it assumes that the best way to improve code is to decreases multiple code attribute measures to below $t_i$ in order
	to remove the ``bad'' smells. In reality, the associations between static code measures are more intricate, for example,
	such that {\em decreasing}  $a_i$ may necessitate {\em increasing} $a_j$.
	It is easy to see why this is so.
% 	A requirement for  code reorganization is that the new code supports the same functionality
% 	as before. 
	For example, Fowler recommends that the Large Class smell be addressed by the Extract Class or Extract Subclass refactoring~\cite{fowler99}. If we pull code out of a function since that function has grown too
	large, that functionality has to go somewhere else. Thus, when \textit{decreasing} lines of code in one module, we may \textit{increase} its coupling to another module. XTREE's identifies such associations between metrics, thus avoiding the conjunctive fallacy.
% 	recommendation is that if we decrease a module's lines of code  then in the reorganized
% 	code, the functionality is achieved via a communication between several different parts
% 	of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
% 	that module's coupling metrics.

	\subsection{Research Questions}

	This paper  claims that (a)~XTREE is more useful than \eq{df} to identify code reorganizations, and (b)~XTREE recommends a small subset of static code measures to change and thus can be used to identify superfluous code reorganizations (i.e., reorganizations based on omitted
	static code measures). To evaluate these claims, we compared the performance of XTREE with three other methods for recommending code reorganizations~\cite{Shatnawi10,Alves2010,me12c} according to the following research questions:

% 	In support of these claims, 
% 	the rest of this paper is structured as follows. In Section~2, we offer some background on bad smells. In Section~3, 
% 	different methods are presented for determining when code does/does not have bad smell. One of those methods
% 	will be XTREE while the others will come from other researchers. Section~4 contains the methods used in this study, the results of which are shown in  . Those results will answer five research questions.

	{\bf  RQ1: Effectiveness}: According to the verification oracle, which of the methods is most accurate in recommending code reorganizations that result in reduced numbers of defective files? 
% 	is the best  change oracle for identifying what and how	code modules should be changed? 
To answer this question, we used data from five OO Java projects
	(Ivy, Lucene, Ant, Poi, Jedit). It was found that:
	\begin{lesson}
		XTREE is the most accurate oracle on how to change code modules in order to reduce the number of defective files.
	\end{lesson}

	{\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
	ignore irrelevant bad smell detectors.  If the recommended changes are minimal (i.e. affect fewest attributes) then those changes
	will be easiest to apply and monitor. Which method recommends changes to the fewest
	code attributes?
	\begin{lesson}
		Of all the code change oracles studied, XTREE recommends changes to the fewest number of static code measures.
	\end{lesson}

	{\bf RQ3: Stopping}: Our goal is to discourage code reorganization based on changes that lack
	historical evidence of being effective. How effective is XTREE at identifying what {\em not} to change?
	\begin{lesson}
		In  any  project,  XTREE's  recommended  changes  to 1--4 
		of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
		would hence be deprecated.
	\end{lesson}

	{\bf RQ4: Stability}: Across different projects, how consistent are the changes recommended by our best change oracle?
	\begin{lesson}
		The direction of change recommended by XTREE (e.g., to LOWER lines of code while RAISING coupling) is stable across repeated runs of change oracle.  
	\end{lesson}

	{\bf RQ5: Conjunctive Fallacy}:  
	Is it always  useful  to apply \eq{df}; i.e. make code better by   reducing the values of  multiple code attributes? We find that:
	\begin{lesson}
		XTREE usually recommends reducing lines of code (size of the modules).
		That said,  XTREE often recommends {\em increasing} the values of other static code attributes.
	\end{lesson} 
	Note that {\bf RQ3, RQ4, RQ5} 
	confirms the intuitions
	of the project managers that prompted this investigation. We find evidence that:
	\bi
	\item Code reorganizations that decrease multiple measures may not yield improvement, In fact,  programmers may need to {\em decrease} some measures while {\em increasing} others.
    \item In the studied projects, XTREE recommends changes to approximately 20\% of the code measures, and thus reorganizations based on the remaining 80\% are unlikely to provide benefit.
    \ei
%     one-fifth  
% 	of the measures were usually found within  change recommendations. That is, it is 80\%\footnote{Isn't it 20\% likely that you will find a useful measurement?} likely that
% 	that code reorganization based on reducing any one measurement picked at random will be useful.
%     \ei
% 	\bi
% 	\item
% 	Yes,  indeed, their programmers
% 	were wasting time on   performing code reorganizations  that  decreased multiple measures when, in fact,
% 	they should be trying to {\em decrease} some measures while {\em increasing} others.
% 	\item
% 	Across all studied projects, XTREE found that  around one-fifth  
% 	of the measures were usually found within  change recommendations. That is, it is 80\% likely that
% 	that code reorganization based on reducing any one measurement picked at random will be useful.
% 	\ei
	Consequently, we  recommend the following use case for  XTREE:
	\bi
	\item Before doing  code reorganization based on a bad smell report...
	\item ...check and discourage any code reorganization   for which there is no proof
	in the historical record that the change improves the code.
	\ei
	This use case described  applies to both manual code reorganizations proposed by developers
	as well as the code reorganizations conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
	code reorganization by discouraging reorganizations for useless goals.

	\subsection{Relationship to Prior Work }
	A four page preliminary repor\footnote{https://goo.gl/2In3Lr}t on the XTREE system has been presented previously~\cite{krishna2015actionable}. That short report offered case studies on only two  of
	the five data sets studied here. We greatly expand on this prior work by:
	\bi
	\item
	Evaluating XTREE's recommendations against recommendations from three others methods by researchers exploring bad smells.
	\item
	Evaluating if XTREE's and other methods' recommended changes were sensible using the {\em secondary verification oracle}
	\ei
	Only sections 3.2.1, 3.2.2, and two-fifths of the results in \fig{jur} contain material
	found in prior papers.

@@

	Much research endorses code smells as a guide for
	code improvement (e.g., code reorganization or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
	lists dozens of papers on smell detection and repair tools. 
	Yet
	other papers cast doubt on the value of bad smells
	as triggers for code improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}. 
	As we show in this paper,  
	tools, text books, and developers disagree on what bad smells
	are important enough to hunt down and eliminate. Our findings
	are consistent with other research suggesting that universal bad
	smells that ignore project context are not useful to guide code reorganizations~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

	If the SE literature is contradictory, why not ignore it and use domain experts (software engineers) to decide
	what bad smells to fix? We do not recommend this since developer {\em cognitive biases} can mislead them to
	assert that some things are important and relevant when they are not. 
	A widespread malaise in software engineering is that
	beliefs about software are rarely revised and hence may be
	inaccurate and 
	misleading~\cite{passos11,jorgensen09,mei15,me16phase,prem16}. Software developers may have strong views on many issues, including bad smells, but those views may be wrong for the current
	project.
	Software engineering is not the only field with this problem.
	For example, the medical profession applies many practices based on studies that have been disproved (a recent article in the Mayo Clinic Proceedings~\cite{prasad13} found 146 medical practices based on studies in year i, but which were reversed by subsequent trials within years i + 10). Even when the evidence for or against a treatment or intervention is clear, medical providers and patients may not accept it~\cite{aschwanden10}. Aschwanden~\cite{aschwanden15} warns that {\em cognitive biases} such as confirmation bias (the tendency to look for evidence that supports what you already know and to ignore the rest) influence how we process information.

@@

	\bi
	% COMMENT FROM LL: This bullet is weak. Maybe goto isn't used in an unrestricted manner because of Djikstra's warning.
	% \item
	% Nagappan et al. analyzed~\cite{mei15} 
	% how   {\tt goto}  was used  in 11,000 Github repositories. 
	% They found that developers
	% rarely used {\tt goto} in the unrestricted manner that alarmed Dijkstra in his  1968
	% memo ``Go to statement considered harmful''~\cite{Dijkstra68}.
	\item
	In other work~\cite{me16phase} with the Software Engineering Institute (SEI), we have revisited
	the ``phase delay'' truism that {\em the cost of fixing an error dramatically increases the longer it is in the system}. 
	We found no evidence for such large   phase delay effect in modern
	software (in 171 software projects shepherded
	by the SEI, 2006-2014) possibly since it has been  heavily mitigated by $21^{st}$ century software development languages, tools and development practices. 
	Whatever the reason, the main point  is that phase delay is a widely
	held belief, despite little recent evidence to support it.
	\item
	Devanbu et al. examined responses from 564 Microsoft software developers from around
	the world, they found that  ``(a)~programmers do indeed have very
	strong beliefs on certain topics; (b)~their beliefs are primarily formed
	based on personal experience, rather than on findings in empirical
	research; (c)~beliefs can vary with each project, but do not necessarily
	correspond with actual evidence in that project''~\cite{prem16}.
	\ei
	Devanbu et al. further  comment that ``programmers give personal experience
	as the strongest influence in forming their opinions''. This is troubling
	especially given the comments from Passos and J{\o}rgensen et al.~\cite{passos11,jorgensen09} about how quickly practitioners form, freeze, and rarely revisit those opinions.

@@

	If the above remarks hold true for bad smells, then we would expect
	to see much disagreement on which bad smells are important and relevant
	to  a particular project. This is indeed the case.
	The first column of \fig{smells} 
	lists  commonly mentioned bad smells and comes from Fowler's 1999 text~\cite{fowler99} and a subsequent 2005 text by Kerievsky that is widely cited~\cite{Kerievsky2005}.
	The other
	columns show data from other studies on which bad smells matter most.
	The columns marked as Lanza'06 and Yamashita'13 are from peer reviewed literature. The column marked SonarQube is a popular open source
	code assessment tool that includes detectors for six of the bad smells
	in column one. 
	The {\em developer survey} (in the right-hand-side column) shows the results of an hour-long whiteboard sessions with a group of 12 developers from a Washington
	D.C. web tools development company. Participants
	worked in a round robin manner to rank the bad smells they thought were
	important (and any disagreements were discussed with the whole group).
	Amongst the group, there was  some
	consensus on  the priority of which bad smells to fix
	(see the annotations VH=very high,
	H=high, L=low, VL=very low, and ``?''= no consensus).

@@

	A  blank cell in \fig{smells}
	indicates where   other work omits 
	one of the bad smells in column one. 
	Note that most of the cells are blank, and that the studies omit the majority of the Fowler bad smells.
	SonarQube has no detectors for many of the column one bad smells.
	Also, nearly half the Yamashita list of bad smells
	does not appear in column 1. The eight numbers
	in the  Yamashita'13 column show the rankings for the bad smells 
	that overlap with Fowler and Kerievsky; Yamashita also discussed other smells not covered in Fowler'99~\cite{fowler99}.

	Two of the studies in \fig{smells} offers some comments on the relative importance
	of the different bad smells. Three of the bad smells listed in the top half of the Yamashita'13 rankings also score very high in the developer survey. Those three were {\em duplicated code, large class}, 
	and {\em long method}. 
	Note that this agreement also means that the
	Yamashita'13 study and the developer survey   
	believe
	that very few  code smells are   high priority issues
	requiring code reorganization.

@@

	Having made the case for automated, evidence-based support for assessing bad smells,
	this section reviews different ways for building those tools (one of those tools,
	XTREE, will be our recommended {\em primary change oracle}).
	Later in this paper, we describe  a {\em secondary verification oracle}
	that checks the effectiveness of the proposed changes.

	The SE literature offers two ways of learning bad smell thresholds.
	One approach relies on 
	{\em outlier statistics}~\cite{erni96,bender99}. This approach
	has been used   by Shatnawi~\cite{Shatnawi10}, Alves et al.~\cite{Alves2010}
	and Hermans et al.~\cite{hermans15}.
	Another approach is 
	based on {\em cluster deltas} that we developed
	for   Centroid Deltas~\cite{me12c} and 
	use here for XTREE. 
	These two approaches are discussed below.

@@

@@

	\subsubsection{ Shatnawi}\label{sect:shatnawi}
	Shatnawi~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
	is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
	constants to compute the thresholds which, following Shatnawi's guidance, we set to
	$p_0=p_1=0.05$.
